Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-05 scripts/03_clustering.Rmd
DOC 03_clustering.Rmd

A common question that arises when performing clustering is how to choose the
number of clusters.

>>>>

A common question that arises when performing clustering is how to choose the
number of clusters. A choice for the number of clusters K depends on the goal. 
In this particular case, the end goal is not the clustering, but to facilitate
interpretation of the differential expression analysis step. As a result, the
number of clusters should not exceed the number of gene sets the user wants to
interpret. This allows to set a maximum number of clusters. Let us assume here
that this number is 20 clusters.

Once the maximum number of clusters is set, several strategies allow to
identify the number of clusters:

    - *Within cluster similarity as a function of the number of cluster* XXX
      GAP statistics
    - *Stability analysis*: this method assumes that the results of the
      clustering will be more stable for the "true" number of clusters than
      for other number of clusters.
